---
title: "Data Visualizations"
author: "Brian Anderson"
output:
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
                      fig.align = "center", fig.width = 5, fig.height = 3)
```

## Load Libraries

```{r}
library(tidyverse)
library(broom)
library(margins)
```

## Simulated Data

Lets set some values, and we'll simulate a 500 observation dataset.

$$y = 2.5 + .65x + 1.5m + .85xm + .5c + \mathcal{N}(0,3)$$

```{r}
# Set our (quasi) random number generator seed
set.seed(1)

# Set our number of observations
obs <- 500

# Define our model parameters 
a <- 2.5
b_x <- .65
b_m <- 1.5
b_xm <- .85
b_c <- .5

df <- tibble(x = rnorm(obs, 0, 2),  # Gaussian (normal) distribution
             m = rbinom(obs, 1, .4),  # Bernulli (binomial) distribution
             c = rpois(obs, 15),  # Poisson distribution
             y = a + (b_x * x) + (b_m * m) + (b_xm * (x * m)) + (b_c * c) + 
               rnorm(obs, 0, 3))

df
```

## Interaction Model

```{r}
y.model <- lm(y ~ x * m + c, data = df)
summary(y.model)
```

## Basic Visualizations

### Bar Chart

```{r}
ggplot(data = df, aes(x = m)) +
  geom_bar()
```

### Data summary

```{r}
df %>% 
  count(m)
```

## Tidy Bar Chart

```{r}
tidy.box <- ggplot(data = df %>% 
                     mutate(m = as_factor(m)), 
                   aes(x = m, fill = m)) +
  geom_bar() + 
  geom_text(stat = 'count', aes(label = ..count..), vjust = 2) + 
  scale_x_discrete(breaks = c("0", "1"),
                   labels = c("Women", "Men")) + 
  scale_fill_discrete(name = "Gender",
                      breaks = c("0", "1"),
                      labels = c("Women", "Men")) + 
  labs(title = "Sample Skews Towards Women",
       subtitle = "N = 500",
       y = "Number of Observations",
       x = "") + 
  theme_bw()

tidy.box
```

### Save the Plot

```{r}
ggsave("TidyBox.png", tidy.box, width = 6, height = 4)
```

## Scatterplot

```{r}
ggplot(data = df, aes(y = y, x = x)) + 
  geom_point() +
  geom_smooth(method = "lm")
```

## Bubble Chart

This incorporates the dichotomous mediator...

```{r}
ggplot(data = df %>% 
         mutate(m = as_factor(m)),
       aes(y = y, x = x, size = m)) + 
  geom_point(alpha = .1) + 
  theme_bw()
```

## Plotting Simnple Slopes

### Create New Dataframe

```{r}
# M = 0 condition
m.0 <- tibble(x = seq(min(df$x), max(df$x), .1),
              m = 0)

# M = 1 condition
m.1 <- tibble(x = seq(min(df$x), max(df$x), .1),
              m = 1)

# Bind the dataframes together
m.df <- bind_rows(m.0, m.1) %>% 
  mutate(c = mean(df$c))

m.df
```

### Create predicted values

```{r}
y.pred <- augment(y.model, newdata = m.df)
y.pred
```

### Quantify Uncertainty

```{r}
y.pred <- y.pred %>% 
  mutate(lower.ci = .fitted - (1.96 * .se.fit),
         upper.ci = .fitted + (1.96 * .se.fit)) %>% 
  mutate_if(is.numeric, funs(round(., 2)))

y.pred
```

### Build the Plot

```{r}
ggplot(data = y.pred %>% 
         mutate(m = as_factor(m)), 
       aes (y = .fitted, x = x, group = m)) + 
  geom_line(aes(linetype = m)) + 
  geom_ribbon(alpha = .2, aes(ymin = lower.ci, ymax = upper.ci)) +
  scale_linetype_discrete(name = "Gender",
                          breaks = c("1", "0"),
                          labels = c("Men", "Women")) + 
  labs(title = "Y Increases More Among Men As X Increases",
       subtitle = "N = 500",
       y = "Predicted Values of Y",
       x = "Range of Meaningful Values of X",
       caption = "95% Confidence Interval in Grey") + 
  theme_bw()
```

## Multilevel Data

```{r}
rnd.df <- read_csv("https://www.drbanderson.com/data/FirmRND.csv")
rnd.df
```

Wrangling...

```{r}
# Industries...
# 3570 - Computer & Office Eqpmt
# 3571 - Electronic Computers
# 3572 - Computer Storage Devices
# 3576 - Computer Communications Eqpmt
# 3577 - Computer Peripheral Eqpmt
# 3578 - Calculating & Accounting Machines
# 3579 - Office Machines

rnd.df <- rnd.df %>% 
  mutate(SICCode = as_factor(SICCode))
```

What are we looking at?

```{r}
rnd.df %>% 
  summarise(NumberFirms = n_distinct(FirmID))
```

```{r}
rnd.df %>% 
  distinct(Year)
```

Lets create a couple of variables...

```{r}
rnd.df <- rnd.df %>% 
  mutate(ROS = 100 * (NetIncome / Revenue),
         RNDIntensity = 100 * (RND / Revenue)) %>% 
  filter(ROS > -50,
         RNDIntensity < 100)  # Eliminate outliers
```

## Visualizations

### R&D Intensity Over Time By Firm

```{r}
ggplot(rnd.df, aes(y = RNDIntensity, x = Year)) + 
  geom_line(aes(group = FirmID), alpha = 1/10) + 
  geom_smooth(method = "loess", se = FALSE)
```

### ROS Over Time By Firm

```{r}
ggplot(rnd.df, aes(y = ROS, x = Year)) + 
  geom_line(aes(group = FirmID), alpha = 1/10) + 
  geom_smooth(method = "loess", se = FALSE)
```

### ROS & R&D By Industry

```{r}
ggplot(rnd.df, aes(y = ROS, x = RNDIntensity)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  facet_wrap(~ SICCode)
```

### Data Summaries

```{r}
ggplot(data = rnd.df %>% 
         group_by(SICCode, Year) %>% 
           summarise(meanRND = median(RNDIntensity)),
       aes(y = meanRND, x = Year, group = SICCode)) + 
  geom_line(aes(linetype = SICCode)) + 
  scale_linetype_discrete(name = "SIC Code") + 
  labs(title = "Median R&D Intensity of 35x Industries",
       subtitle = "2013 - 2017",
       y = "Median R&D Intensity",
       x = "") + 
  theme_bw()
```

