---
title: "Intro to R Live Coding"
author: "Brian Anderson"
output:
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
                      fig.align = "center", fig.width = 5, fig.height = 3)
```

## Libraries

How to install a package (library)

```{r, eval = FALSE}
install.packages("tidyverse")
```

Once installed, they are always there, but to access the library in a session, you need to load it into memory.

```{r}
# Load library into memory
library(tidyverse)
```

## Simulated Data

There are lots of ways to load data into R---basically, any type of data from any source can find its way into R. For our purposes, we're going to create our own.

Lets create data from a multiple regression model:

$$y = \alpha + \beta_x + \beta_w + \epsilon$$

Lets set some values, and we'll simulate a 200 observation dataset.

$$y = 3.5 + .65_x + .3_w + \mathcal{N}(0,3)$$

```{r}
set.seed(1)
obs <- 200

df <- tibble(x = rnorm(obs, 0, 2),
             w = rnorm(obs, 0, 3))

df
```

Next lets create our outcome variable:

```{r}
# Define our model parameters 
a <- 3.5
b_x <- .65
b_w <- .3

df <- df %>% 
  mutate(y = a + (b_x * x) + (b_w * w) + rnorm(obs, 0, 3))

df
```

## Basic Visualizations

```{r}
ggplot(data = df, aes(y = y, x = x)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  geom_smooth(method = "loess", color = "red") +  
  theme_bw()
```

## Linear Model

```{r}
y.model <- lm(y ~ x + w, data = df)
summary(y.model)
```

## Regression Diagnostics

### Install a new package

```{r, eval = FALSE}
install.packages("ggfortify")
```


```{r}
library(ggfortify)
autoplot(y.model)
```

## Formatting Results

### Tidying Model Results

```{r, eval = FALSE}
install.packages("broom")
```

Creating a manipulable dataframe

```{r}
library(broom)
y.tidy <- tidy(y.model)
y.tidy
```

### Formatting Results Tables

```{r, eval = FALSE}
install.packages("sjPlot")
```

Create an html table for copy and pasting...

```{r, eval = FALSE}
library(sjPlot)
tab_model(y.model)
```

## Summary Statistics

A note on correlation matrices.

### Descriptive statistics

```{r, eval = FALSE}
install.packages("skimr")
```

```{r}
library(skimr)
skim(df)
```


